A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-08-29 paper/project.tex
Comparing resolutions, improving resolution density plot

The majority of the empirical parameters used in our functional are
taken from the paper of Clark \emph{et al} on developing an optimal
SAFT model for water\cite{clark2006developing}.  This SAFT model
contains five empirical parameters: the hard-sphere radius, an energy
and length scale for the dispersion interaction, and an energy and
length scale for the association interaction.  In addition to the five
empirical parameters of Clark \emph{et al}, we add a single additional
parameter defining the length scale over which the density is averaged
when computing the dispersion free energy.  We use this final
parameter to fit the surface tension, with the result shown in
Figure~\ref{fig:surface-tension}.  Because the SAFT model of Clark
\emph{et al} in overestimates the critical temperature---which is a
common feature of models which do not explicitly treat the critical
point---we cannot correctly describe the surface tension at all
temperatures, and chose to fit it for the temperature range at which
water is liquid at one atmosphere of pressure.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-vs-radius}
\end{center}
\caption{ Density profiles for 
a single hydrophobic rod with a radius of 0.5 nm using several different 
lattice spacing resolutions. high = 0.05 bohrs, 
med = 0.2 bohrs, low = 0.5 bohrs }
\label{fig:densityresolution}
\end{figure}

>>>>

The majority of the empirical parameters used in our functional are
taken from the paper of Clark \emph{et al} on developing an optimal
SAFT model for water\cite{clark2006developing}.  This SAFT model
contains five empirical parameters: the hard-sphere radius, an energy
and length scale for the dispersion interaction, and an energy and
length scale for the association interaction.  In addition to the five
empirical parameters of Clark \emph{et al}, we add a single additional
parameter defining the length scale over which the density is averaged
when computing the dispersion free energy.  We use this final
parameter to fit the surface tension, with the result shown in
Figure~\ref{fig:surface-tension}.  Because the SAFT model of Clark
\emph{et al} overestimates the critical temperature---which is a
common feature of models which do not explicitly treat the critical
point---we cannot correctly describe the surface tension at all
temperatures, and chose to fit it for the temperature range at which
water is liquid at one atmosphere of pressure.

@@

Figure \ref{fig:densityresolution} shows the density profiles for three different
values of the lattice spacing resolution. The density oscillations outside a single
rod of radius 0.5 nm look nearly identical for all resolutions except for the first peak. 
This contact density is important to get correct as it \fixme{relates to energy}. The 
contact density calculated using the medium resolution is within 3.5\% of the value at
high resolution, while the low resolution contact density is only within 5.1\%. The total
free energy calculations compare much more favorably. The medium resolution is within 
0.5\% and the low resolution is within 1.0\% of the high resolution free energy.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-vs-radius}
\end{center}
\caption{ Density profiles for 
a single hydrophobic rod with a radius of 0.5 nm using several different 
lattice spacing resolutions. We used a high resolution of 0.05 bohrs ($\approx$ 0.003 nm), 
medium 0.2 bohrs ($\approx$ 0.001 nm), and low 0.5 bohrs ($\approx$ 0.03 nm).}
\label{fig:densityresolution}
\end{figure}
